### 2015-01-15 src/analysis.Rnw
operator samples
update1

@@

\begin{table*}[!ht]
\caption*{Single Operators}
<<results='asis'>>=
print(xtable(s.singles.db, caption='Single Operators', label='table:singles'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The n-selection criteria results}
\label{tbl:lcountl}
\end{table*}

\section{Analysis}
\label{sec:analysis}
For the purposes of comparing between the criteria, we computed the
linear correlation between sampled mutation score and full mutation score.
Since for the baseline sampling criteria, no mutants sampled implies none generated,
our model was
\[\mu\{M_{all}|M_{reduced}\} = \beta_1 \times M_{reduced}\]
where $M_{all}$ is the mutation score of original mutation analysis and
$M_{reduced}$ is the mutation score of the sample.

We reported the correlation for this linear regression. We also report the expected
multiplier factor $\beta_1$ for the sampled mutation score. This factor
determines the ease of detecting mutants in the sampling criteria. That is, if the
multiplier factor is small, then the sample mutation score was larger than
the full mutation score, and hence it was easier to detect mutants in the sample.

Next, for each criterion, we computed the reduction of mutants given by the
ratio between sampled mutants and total number of mutants.
We also compute standard deviation of the mutant reduction, which determines
the consistency of results. A large standard deviation suggests
that the mutant reduction ratio achieved is very much dependent on the
project. Therefore, as a heuristic, we suggest looking at only those methods which
have a mean reduction ratio at least twice the standard deviation.

A few projects did not return any results for some large reduction factors.
Thus the number of valid results from projects is also collected in the result
tables.

>>>>

\begin{table*}[!ht]
\caption*{Single Operators}
<<results='asis'>>=
print(xtable(s.singles.db, caption='Single Operators', label='table:singles'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The single operator selection results}
\label{tbl:lcountl}
\end{table*}

\begin{table*}[!ht]
\caption*{Operator Samples x\%}
<<results='asis'>>=
print(xtable(s.opsample.db, caption='Operator x samples', label='table:opsample'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The operator x\% sample criteria results}
\label{tbl:lcountl}
\end{table*}

@@

\section{Analysis}
\label{sec:analysis}
For the purpose of comparing different mutation reduction strategies, we
computed the average \textit{test utility}, and \textit{assert utility} of
different strategies.

We use the mutant reduction strategy to select a subset
of mutants from the original set. We then collect all test cases that were
able to kill any of the selected set of mutants. Next we compute the
non-redundant test cases by discarding any test case that can be removed
without letting any of the mutants escape. This is repeated $10$ times,
and the average number of non-redundant test cases are found.

While computing the test cases, we also collect assertion number each
test case has. We compute this as the number of asserts in the test case
incremented by one to account for test cases without any asserts. Thus the
compute both the assertions from non-redundant test cases for the mutant
selection, and also the assertions for the full set of killing test cases
for the mutant selection.

The \textit{test utility} is computed as the difference between the number
of non-redundant test cases the mutant selection achieved and the number of
non-redundant test cases of a random sample of same number of mutants.
The result is reported as a percentage of the non-redundant tests of the random
sample (the baseline).

Similarly \textit{assert utility} of a strategy is computed

### 2015-01-15 src/introduction.Rnw
update1

Selective mutation strategies attempt to select a representative
subset of mutation \emph{operators} based on heuristics and
statistical analysis, and apply this subset of operators to generate
mutants instead of applying the whole set of mutation
operators~\cite{offutt1993anexperimental,untch2009onreduced}.
Recent work suggests that using statement deletion alone can
be an effective approach~\cite{untch2009onreduced}.

Sampling strategies seek to randomly select a set of representative
mutants.  This was investigated first by
Acree~\cite{acree1980mutation} and Budd~\cite{budd1980mutation}, who
proposed using only $x$\% of all mutants produced. Wong and Mathur
found that random sampling with ratio as low as 10\% could provide
accurate results~\cite{jia2011analysis}.

@@

We have attempted to rectify this situation with a large scale study of real
world programs. As detailed in Section~\ref{sec:methodology}, we sample
312 Java programs from Github, with size ranging from $50$ to $100,000$
lines (excluding tests), allowing us to draw more widely applicable
statistical inferences.

@@

If we assume that testers would prefer adding test cases that increases the
mutation score, then a good strategy should reward the behavior of adding
non-redundant test cases and test suites with larger number of asserts.
Thus it should choose a set of mutants that are killed by a larger number
of such non-redundant tests at-least in comparison with random selection
of the same number of mutants as the chosen set. We could also ensure that
a reduction strategy does not miss out on important tests by running the
set of non-redundant tests against the full set of mutants to see how many
of the mutants were detected in comparison with the original number of
detected mutants. Since this evaluation crtieria does not depend on the
mutation-adequacy of the test suite under consideration, we can run the
evaluation using real world projects which almost always have non-adequate
test suites.

>>>>

Selective mutation strategies attempt to select a representative
subset of mutation \emph{operators} based on heuristics and
statistical analysis, and apply this subset of operators to generate
mutants instead of applying the whole set of mutation
operators~\cite{offutt1993anexperimental,untch2009onreduced}.
%Recent work suggests that using statement deletion alone can
%be an effective approach~\cite{untch2009onreduced}.

Sampling strategies seek to randomly select a set of representative
mutants.  This was investigated first by
Acree~\cite{acree1980mutation} and Budd~\cite{budd1980mutation}, who
proposed using only a small fraction of randomly selected mutants.
Wong and Mathur found that random sampling fraction as low as 10\%
could provide accurate results~\cite{jia2011analysis}.

@@

We have attempted to rectify this situation with a large scale study of real
world programs. As detailed in Section~\ref{sec:methodology}, we sample
$312$ Java programs from Github, with size ranging from $50$ to $100,000$
lines (excluding tests), allowing us to draw more widely applicable
statistical inferences.

@@

If we assume that testers would prefer adding test cases that increases the
mutation score, then a good strategy should reward the behavior of adding
non-redundant test cases and test suites with larger number of asserts.
Thus it should choose a set of mutants that are killed by a larger number
of such non-redundant tests at-least in comparison with random selection
of the same number of mutants as the chosen set. We could also ensure that
a reduction strategy does not miss out on important tests by running the
set of non-redundant tests against the full set of mutants to see how many
of the mutants were detected in comparison with the original number of
detected mutants. This can again be compared to the test cases selected by
a random sample of same number of mutants to see if the strategy performed
better at-least with respect to random sampling. Since this evaluation crtieria
does not depend on the mutation-adequacy of the test suite under consideration,
we can run the evaluation using real world projects which almost always have
non-adequate test suites.
